### 2015-02-20 fundamentals/impl.tex
weird sentence pain
sentence getting more readable
simplicity is beauty

Simulation science - like experimental science - must identify trustworthy
results from nonsensical results or noise.
Charles Babbage famously articulated this, ``On two occasions I have been asked,
`Pray, Mr. Babbage, if you put into the machine wrong figures, will the right
answers come out?' ... I am not able rightly to apprehend the kind of confusion
of ideas that could provoke such a question.'' \cite{babbage_passages_2011}.
A simulator must assure correctness and guard against the \emph{garbage
in, garbage out} phenomenon.

Multiple strategies, collectively known as \emph{\gls{QA}}, have
been invented over the years to mitigate the structural and algorithmic errors
on the part of simulators themselves. These include \emph{\gls{VV}}
\cite{boehm_software_1989}, \emph{\gls{UQ}}
\cite{sacks_design_1989}, testing, and others. \gls{VV} and \gls{UQ} come from
a distinctly computational science background while testing \emph{et al.} come from software development.

>>>>

Simulation science - like experimental science - must distinguish trustworthy
results from untrustworthy ones.
Charles Babbage famously articulated this, ``On two occasions I have been asked,
`Pray, Mr. Babbage, if you put into the machine wrong figures, will the right
answers come out?' ... I am not able rightly to apprehend the kind of confusion
of ideas that could provoke such a question.'' \cite{babbage_passages_2011}.
A simulator must assure correctness and guard against the \emph{garbage
in, garbage out} phenomenon.

Multiple strategies, collectively known as \emph{\gls{QA}}, have
been invented to mitigate the structural and algorithmic errors
in software. These include \emph{\gls{VV}}
\cite{boehm_software_1989}, \emph{\gls{UQ}}
\cite{sacks_design_1989}, testing, and others. \gls{VV} and \gls{UQ} come from
a distinctly computational science background while testing \emph{et al.} come from software development.
